Appendix C: Latent Class Growth Analysis

### 2023-01-31 appendix_c.Rmd

@@

>>>>

It is important to highlight that in LCGA, the subgroups will be limited by
the specify growth structure, meaning that LCA will identify distinctive
growth patterns within the intercept, step, and slope growth. For
example, if there is a subgroup that follows a quadratic growth pattern
this models will not be able to identify it.

@@

## R session

```{r echo = TRUE, eval=TRUE}
sessionInfo()
```
